Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-12 paper/ijcai/paper.tex
pass on section 3.0

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available.

@@

In the following, we illustrate the workflow of the \sfl{}+\cs{}
combination for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the \sfl{}+\cs{} 
combination consists of four steps:\Sof{Should we specify that these steps are
performed for each version of the projects/defect?}

@@

Intuitively, slicing enables identification of cells in the spectra
whose values can be set to zero, \ie{}, the components marked with 0
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one can observe that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the example from
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

It is possible that a slice that discards the faulty component still
produces the expected message checked by the oracle. This can happen,
for example, if the oracle is too
general. Section~\ref{sec:oracleheuristics} elaborates the heuristics
we used to mitigate this fundamental limitation of Critical Slicing.

@@

\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}

>>>>

\Mar{consider moving footnotes 1 and 2 to references.}
Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available.

@@

In the following, we illustrate the workflow of the \sfl{}+\cs{}
combination for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\sfl{}+\cs{} combination consists of four steps: \Sof{Should we
  specify that these steps are performed for each version of the
  projects/defect?}\Mar{Isn't this clear from the scenario in the
  beginning of par?  Note that this is the definition of the workflow
  for the technique, not the definition of the experiment (when it
  makes sense to talk about versions/defects and D4J.)}

@@

Intuitively, slicing enables identification of cells in the spectra
whose values can be set to zero, \ie{}, the components marked with 0
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the example from
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

Conceptually, if the oracles implemented in faulty tests are too
general, the critical slicing algorithm could produce slices without
the faulty code. For example, consider the scenario of an unexpected
Null-Pointer Exception (NPE) thrown in the code. If the oracle checks
for the presence of NPE regardless of where it occurs, it is possible,
in principle, that the final slice does not include the faulty code
but still raises NPE (in a different part of the code). The critical
slicing algorithm would consider that as an acceptable simplification
and would continue. Section~\ref{sec:oracleheuristics} shows how we
mitigate this fundamental limitation of Critical Slicing and
Section~\ref{sec:fault-misses} shows how problematic is that issue in
practice.

@@

\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
\label{sec:fault-misses}
